Constraints on Cosmic-Ray Particle Populations, Magnetic Fields, and Dark Matter from VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS

### 2011-06-13 ms.tex
Added theta^2 and sig dist plots and updated the skymaps

@@

The ring background model \citep{article:Aharonian_etal:2001} is used to estimate the background due to CRs. The total number of events in a given region of interest is then compared to the estimated background from the off-source region scaled by the ratio of the solid angles to produce a final excess. The VHE gamma-ray significance is then calculated using the method by \citet{article:LiMa:1983}.  Significance skymaps over the VERITAS field of view are shown in Figure \ref{fig:Coma:skymaps} with overlaid X-ray and radio contours from the ROSAT all-sky survey \citep{article:BrielHenryBohringer:1992}  and GBT 1.4 GHz observations \citep{article:BrownRudnick:2010} respectively.

\begin{figure*}
\begin{center}
\scalebox{0.5}{\plotone{f1a.eps}}
\scalebox{0.5}{\plotone{f1b.eps}}
\end{center}
\caption{Skymaps.}
\label{fig:Coma:skymaps}
\end{figure*}

\section{Results}
No significant excess was detected with VERITAS in the Coma cluster.
A 99\% confidence level upper limit is calculated for each region of interest using the method described by \citet{article:Rolke:2005} and assuming Gaussian background.

\begin{deluxetable}{lccccccc}
\tablecolumns{7}
\tablewidth{0pc}
\tablecaption{Flux upper limits for regions of interest in the Coma cluster of galaxies.}
\tablehead{
\colhead{Source} &
\colhead{RA} &
\colhead{Dec} &
\colhead{RoI} &
\colhead{Excess} &
\colhead{Significance\tablenotemark{a}} &
\multicolumn{2}{c}{Flux U.L.\tablenotemark{b}}\\
\colhead{} & \colhead{[J2000]} & \colhead{[J2000]} & \colhead{[deg]} & \colhead{[counts]} & \colhead{[$\sigma$]} & \multicolumn{2}{c}{[$10^{-8}$ ph. m$^{-2}$ s$^{-1}$]}}
\startdata
Core & \RA{12}{59}{48.7} & \Dec{+27}{58}{50.0} & 0 & 17 & 0.84 & 2.62 & (1.3\%)\\
& & & 0.2 & -41 & -1.0 & 1.7 & (0.87\%)\\
& & & 0.4 & -26 & -0.30 & 4.5 & (2.3\%)\\
NGC 4889 & \RA{13}{00}{08.13} & \Dec{+27}{58}{37.03} & 0 & 3 & 0.14 & 2.09 & (1.1\%)\\
NGC 4874 & \RA{12}{59}{35.71} & \Dec{+27}{57}{33.37} & 0 & -14 & -0.71 & 1.42 & (0.72\%)\\
NGC 4921 & \RA{13}{01}{26.12} & \Dec{+27}{53}{09.59} & 0 & -4 & -0.23 & 1.89 & (0.96\%)
\enddata
\tablenotetext{a}{Statistical significance calculated according to \citet{article:LiMa:1983}}
\tablenotetext{b}{99\% confidence level upper limit calculated according to \citet{article:Rolke:2005} above an energy threshold of 220 GeV. Values in parentheses are the corresponding fluxes in percent of the steady Crab Nebula flux.}
\label{table:results}
\end{deluxetable}

>>>>

\usepackage{lscape}

@@

The ring background model \citep{article:Aharonian_etal:2001} is used to estimate the background due to CRs. The total number of events in a given region of interest is then compared to the estimated background from the off-source region scaled by the ratio of the solid angles to produce a final excess. The VHE gamma-ray significance is then calculated using the method by \citet{article:LiMa:1983}.  Significance skymaps over the VERITAS field of view are shown in Figure \ref{fig:skymaps} with overlaid X-ray and radio contours from the ROSAT all-sky survey \citep{article:BrielHenryBohringer:1992}  and GBT 1.4 GHz observations \citep{article:BrownRudnick:2010} respectively.

\begin{figure*}
\begin{center}
\scalebox{0.45}{\plotone{f1a.eps}}
\scalebox{0.45}{\plotone{f1b.eps}}
\end{center}
\caption{\emph{Top}: Smoothed significance map of the Coma cluster calculated from the observed excess VHE gamma-ray events over a $4.5^{\circ}\times 4.5^{\circ}$ field of view. The excess counts were derived using a ring-ring background model \citep{article:Aharonian_etal:2001}. White contours show the X-ray counts per second in the 0.1 to 2.4 keV energy band from the ROSAT all-sky survey \citep{article:BrielHenryBohringer:1992}. \emph{Bottom}: Same as above but with overlaid contours from point source subtracted GBT radio observations at 1.4 GHz \citep{article:BrownRudnick:2010}. Shown are also the $0.2^{\circ}$ and $0.4^{\circ}$ radii (dashed cyan) considered for the extended source analyses presented here.}
\label{fig:skymaps}
\end{figure*}

\section{Results}
No significant excess of VHE gamma-rays from the Coma cluster was detected with VERITAS.

A 99\% confidence level upper limit is calculated for each region of interest using the method described by \citet{article:Rolke:2005} assuming a Gaussian background. Figure \ref{fig:sigdist} shows that the VERITAS data is well fit by a Gaussian with a mean of zero and unit standard deviation. The results are listed in Table \ref{table:results}.

\begin{figure*}
\begin{center}
\scalebox{1.0}{\plotone{f2.eps}}
\end{center}
\caption{$\theta^{2}$ distribution from VERITAS observations of the Coma cluster of galaxies. The points with error bars represent the ON-source data sample and and the filled area the background sample. Each bin represents an annulus around the Coma cluster core position. The data were derived from the ring-ring background model using a $0.2^{\circ}$ sampling radius.}
\label{fig:thetasq}
\end{figure*}

\begin{figure*}
\begin{center}
\scalebox{1.0}{\plotone{f3.eps}}
\end{center}
\caption{Distribution of significance for Figure \ref{fig:skymaps} and a sampling radius of $0.2^{\circ}$. The line is a Gaussian fit to the data, with mean close to zero and almost unit standard deviation.}
\label{fig:sigdist}
\end{figure*}

\begin{landscape}
\begin{deluxetable}{lccccccc}
\tablecolumns{7}
\tablewidth{0pc}
\tablecaption{Flux upper limits for regions of interest in the Coma cluster of galaxies.}
\tablehead{
\colhead{Source} &
\colhead{RA} &
\colhead{Dec} &
\colhead{RoI} &
\colhead{Excess} &
\colhead{Significance\tablenotemark{a}} &
\multicolumn{2}{c}{Flux U.L.\tablenotemark{b}}\\
\colhead{} & \colhead{[J2000]} & \colhead{[J2000]} & \colhead{[deg]} & \colhead{[counts]} & \colhead{[$\sigma$]} & \multicolumn{2}{c}{[$10^{-8}$ ph. m$^{-2}$ s$^{-1}$]}}
\startdata
Core & \RA{12}{59}{48.7} & \Dec{+27}{58}{50.0} & 0 & 17 & 0.84 & 2.62 & (1.3\%)\\
& & & 0.2 & -41 & -1.0 & 1.7 & (0.87\%)\\
& & & 0.4 & -26 & -0.30 & 4.5 & (2.3\%)\\
NGC 4889 & \RA{13}{00}{08.13} & \Dec{+27}{58}{37.03} & 0 & 3 & 0.14 & 2.09 & (1.1\%)\\
NGC 4874 & \RA{12}{59}{35.71} & \Dec{+27}{57}{33.37} & 0 & -14 & -0.71 & 1.42 & (0.72\%)\\
NGC 4921 & \RA{13}{01}{26.12} & \Dec{+27}{53}{09.59} & 0 & -4 & -0.23 & 1.89 & (0.96\%)
\enddata
\tablenotetext{a}{Statistical significance calculated according to \citet{article:LiMa:1983}}
\tablenotetext{b}{99\% confidence level upper limit calculated according to \citet{article:Rolke:2005} above an energy threshold of 220 GeV. Values in parentheses are the corresponding fluxes in percent of the steady Crab Nebula flux.}
\label{table:results}
\end{deluxetable}
\end{landscape}
